\section{Conclusion}
\label{sec:conclusion}

This project developed a concept design for a small and lightweight jumping quadruped robot to be used as a platform for training DRL controllers for jumping, arial stabilization, and landing. 

Through motor selection and Simulink Simscape simulations, motor-only actuation proved inadequate for achieving the desired jump performance. Consequently, integrating torsional springs was essential to store and release energy effectively during jumps.

Grid search optimization identified optimal link lengths that to maximize effective jump height. Optimal link lengths were found to be too long for practical robot construction, so link lengths were chosen according to a trade-off between jump height and robot size. System identification refined motor friction models, enhancing simulation accuracy.

Limitations include the symmetric jumping model's simplifications yielding potentially different optimal link lengths than a more realistic asymmetric jumping model. We have not yet performed hardware tests for jumping, thus we do not know how realistic the simulation results are, given mass, inertia, and friction approximations and unmodeled dynamics. We have not tested if the knee motors are able to give stall torque for long enough to load the springs, without overheating or damaging the motor, which is it assumed they can do in simulation.

Despite these limitations, the project demonstrates that the robot design is capable of sufficient jumping performance for demonstrating DRL controllers for jumping, aerial stabilization, and landing for traversing martian lava tubes.


\subsection{Future work}
The upcoming masters thesis we will performn tests to evaulate real life jumping performance of the simulation derived design, and see if knee motors are able to give stall torque for long enough to load springs maximally. We will also investigate adding hip motor actuation during jumps to enhance performance and enable feedback control. Then we will use our optimized design to construct the physical robot and create an accurate model in Nvidia Isaac Sim. This model will be used to train reinforcement learning controllers for jumping, aerial stabilization, and landing. Domain randomization techniques will help minimize the sim-to-real gap, and curriculum learning will be explored to make the learning process more tractable. Finally, we will evaluate the trained policies on the physical robot in practical jumping scenarios.

Due to the oversights addressed in section \ref{sec:design_motor_only_jumps}, the promising A80BHP-H motor was overlooked when selecting motors. This motor not only has almost twice the stall torque of the current knee motor, it also has twice the operating velocity. Future work will include investigating the jumping capabilities of a robot combining this motor with a torsional spring.
